%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}



\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
     {\small#3} &{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingTop}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\
      {\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://rcyerramsetti.com}{\Large Ramachandra Yerramsetti}} & Email : \href{mailto:rcyerramsetti@protonmail.com}{rcyerramsetti@protonmail.com}\\
  \href{https://github.com/ramchandra3101}{GitHub/ramchandra3101} & \href{https://rcyerramsetti.com}{https://rcyerramsetti.com}
\\
  \href{https://www.linkedin.com/in/ramachandra-yerramsetti-1b2265125/}{Linkedin/Ramachandra Yerramsetti} &Mobile : \href{tel:+19592320757}{+1-959-232-0757} \\ \end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingTop
      {University of Connecticut}{Storrs, CT}
      {Master of Engineering in Computer Science}{Aug. 2023 -- Dec. 2024}
      {\textbf{Coursework:} Machine Learning, Computer Networks, Algorithms \& Complexity}{GPA: 3.2}
    \resumeSubheadingTop
      {Koneru Lakshmaiah (Deemed to be) University}{Vijayawada India}
      {Bachelor of Engineering in Electrical and Electronics}{Aug. 2015-- Jun. 2019}
      {\textbf{Coursework:} Object-Oriented Programming(Java), C  \& Data Structures}{GPA:3.4(8.8/10)}
       %{\textbf{Coursework:} Power Electronics for Renewable Energy , Microprocessors and Microcontrollers }{GPA:3.4(8.8/10)}
  \resumeSubHeadingListEnd





%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Full stack developer(Java)}{Jun. 2022 - July. 2023}
   {Tata Consultancy Services: \textbf{Java, Python, Angular, Kubernetes, CI/CD, Javascript, NodeJS}}{Hyderabad, India}
      
      \resumeItemListStart
                 \resumeItem{Ticket Booking App}
         {Designed and implemented a web and mobile application to book online tickets for SNCB-Belgian rail using AngularJS, driving a 40\% increase in user engagement.}
       
      \resumeItem{Monitoring System} 
         {Achieved 75\% reduction in monitoring time by architecting an advanced Python-based health check monitoring system for over 30 SAP production environments.}
 
         \resumeItem{Performance Tuning}
         {Fine-tuned system efficiency by addressing performance bottlenecks, achieving a marked decrease in execution time for over 100 background processes.}        
        
         \resumeItem{Cybersecurity}
       {Implemented an algorithm for detecting components at risk of cyber attacks, enhancing system security by identifying vulnerabilities.}

        \resumeItem{Changes Movement}
          {Developed a streamlined process for the efficient transfer of change objects across development, testing, QA, and production environments, enhancing project agility and deployment speed by 40\%.}
        %\resumeItem{System installation}
      % {Launched a Linux-based print server for Merck Animal Health's Amsterdam site, seamlessly integrating over 100 printers with SAP in collaboration with Hewlett Packard.}
        
        
       
      \resumeItemListEnd
      
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
       {Full Stack developer}{Jul. 2019 - May. 2022}
      {Cognizant Technology Solutions: \textbf{ReactJS, Javascript, Linux, SQL}}{Chennai, India}
     
      \resumeItemListStart
      
     
          \resumeItem{Reusable Components}
        {Achieved a 40\% enhancement in website speed and performance across a portfolio of 10+ company websites by leveraging React to create reusable components.}
        \resumeItem{Web Development}
        {Attained 100\% client satisfaction by designing website structures and page layouts that precisely met user requirements.}

         \resumeItem{Single page app}
         {Transformed a multi-page user experience into a single-page application (SPA), boosting customer engagement by 10\% through seamless navigation and reduced loading times.}
       \resumeItem{API}
        {Developed app integrations using REST and SOAP APIs for features like Google Maps, social media logins, payment processors, and other services.}
        \resumeItem{ReactJS}
          {Transformed design concepts and wireframes into high-caliber code, crafting intuitive application interfaces using JavaScript within the ReactJS framework, and adhering to established workflows.}
          
                       \resumeItemListEnd

   \resumeSubheading
    {Software Engineer Intern}{Summer 2017 and 2018}
    {Axelta Systems}{Hyderabad, India}
     
   \resumeItemListStart
        \resumeItem{Internet of Things}
       {Developed a Python script on a Raspberry PI platform to ensure 100\% data retrieval from various sensors.}
        \resumeItem{Cloud Dashboard}
         {Created a cloud dashboard for real-time data integration, processing, and analysis resulting 50\% reduction in storage costs.}
   
    \resumeItemListEnd
 \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{\href{https://github.com/ramchandra3101/Cyberinfrastructure-competition}{NSF Cyberinfrastructure Competition-1st Prize}}
      {Achieved first place in the UCONN Cyberinfrastructure Competition with a cross-disciplinary team for predicting Citibike usage in Manhattan using a GRU model and GIS analysis.}
    \resumeSubItem{\href{https://github.com/ramchandra3101/NFLoutcomes-prediction}{NFL Outcome Prediction}}
          {Crafted an ML model for NFL predictions, enhancing accuracy by 40\% with enriched player data from two decades.}
   % \resumeSubItem{KLAD(E-commerce clothing website)}
     % {Built a MERN stack-based e-commerce website for the apparel startup KLAD, enhancing the online shopping experience.}
    \resumeSubItem{Student Mental Health Analysis}
      {Led a project to predict UConn students' mental health outcomes based on social media usage and facilitating support services.}
   \resumeSubItem{US pollution prediction using AQI}
    {Developed a predictive model utilizing deep learning to forecast US pollution levels for individual counties based on the Air Quality Index, achieving a commendable 70\% accuracy rate.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
     \resumeSubItem{\textbf{Languages}}{ Java, Typescript, Javascript, NoSQL}\\
    
     %\resumeSubItem{\textbf{Simulation Softwares}}{MATLAB Simulink}
     \resumeSubItem{\textbf{Web Development}}{Angular, Node, HTML/CSS}\\
     \resumeSubItem{\textbf{Version Control}}{Git, GitHub}\\
    % \resumeSubItem{\textbf{Containerization}}{Docker, Kubernetes}\\
     \resumeSubItem{\textbf{Python Libraries}}{Pandas, Scikit-Learn, NumPy, Tensorflow}\\
     \resumeSubItem{\textbf{Database \& Cloud}}{MySQL, Oracle, MongoDB, AWS}
  \resumeSubHeadingListEnd
%--------Leadership------------
%\section{Leadership}
%\resumeSubHeadingListStart
%\resumeSubItem{Smart India Hackathon 2017}
   %   {Managed a team of 25, mentoring in designing and drafting requirements for the national-level hackathon(Student's Voice) at KL University.}

% \resumeSubHeadingListEnd
 
%-------------------------------------------
\end{document}
